### 2022-12-08 ms.rmd
Adding lnCVR plots for environment

```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR"}
p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), "; P = ", round(model3.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18))

@@

```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR"}
p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", k = FALSE) +annotate("text", x = 1, y = -5, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))

@@

```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations"}

@@

p8.1 / p8.2

>>>>

```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR wild populations"}
p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), "; P = ", round(model3.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18))

@@

```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR wild populations"}
p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", k = FALSE) +annotate("text", x = 1, y = -5, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))

@@

```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}

@@

p8.1.2 <- p8.1 / p8.2

ggsave(p8.1.2, filename = "./output/figures/fig8.png")
```

```{r, fig9, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}

 col <- c("#0871B9", "#F3B40D", "#1BB908")
p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))

p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))

p91.2 <- p9.1 / p9.2

ggsave(p91.2, filename = "./output/figures/fig9.png")
```
